Proportional multi-state multiple-cohort life table model

### 2018-04-18 MSLT/MSLTdoc.Rmd
Generate inputs life table
From produced population numbers, mortality rates and yld rates. TO DO

  }
}

```
Health outcomes included in leisure time meta-analysis: all-cause mortality, cardiovascular disease, stroke, coronary heart disease, total cancer, colon, lung, endometrial, and breast cancer.

>>>>

###Do graph with another layer for original rates in age groups for comparison purposes. 
 # p <- ggplot(data = interpolated, aes(age,rate)) +
 #            geom_line(aes(color = "Interpolated")) 
 #            theme_classic()
 #            print(p)
  }
}

```

15) The following code brings together all the required data to create the inputs life table (Figure 3)

Health outcomes included in leisure time meta-analysis: all-cause mortality, cardiovascular disease, stroke, coronary heart disease, total cancer, colon, lung, endometrial, and breast cancer.
